---
title: "How often Synthometricon shows related scales"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: 'hide'
    self_contained: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE, fig.width = 8, fig.height = 4,
                      fig.path = "output/search_validity/", cache.path = "output/search_validity/cache/")
```

```{r libraries}
library(tidyverse)
library(arrow)
library(glue)
library(knitr)
theme_set(theme_bw())
set.seed(20260929)

model_name <- "ItemSimilarityTraining-20240502-trial12"
study_tags <- c(pilot = "osf-bainbridge-2021-s2-0", validation = "validation-study-2024-11-01")

# Inputs are the published data of the SurveyBot3000 paper, downloaded once into a local cache
data_dir <- "output/search_validity/data"
data_url <- "https://raw.githubusercontent.com/rubenarslan/surveybot3000/327966d194e78699b891bd8620b999d61c7e0ea2/data/intermediate"
embeddings_url <- "https://raw.githubusercontent.com/synth-science/surveybot3000/b7601cc3e97d2cd5be973b3fe93af56bb35b9b7a/validation_study/embeddings_surveybot3000.feather"
fetch <- function(url) {
  dir.create(data_dir, showWarnings = FALSE, recursive = TRUE)
  path <- file.path(data_dir, basename(url))
  if (!file.exists(path)) download.file(url, path, mode = "wb", quiet = TRUE)
  path
}

# From the SurveyBot3000 analysis code (global_functions.R): the first item's key is given, and
# every other item is reverse-keyed if it correlates negatively with the first item
find_reverse_items_by_first_item <- function(rs, first_item_key) {
  items <- rs[-1, 1]
  if (first_item_key == 1) {
    reversed <- which(items < 0) + 1
  } else {
    reversed <- c(1, which(items > 0) + 1)
  }
  colnames(rs)[reversed]
}
```

Synthometricon (formerly SynthNet) lets researchers search APA PsycTests with a set of questionnaire
items. The engine embeds each item with SurveyBot3000, a language model fine-tuned so that the cosine
between two item vectors predicts the correlation between the two items. It represents a scale the
way a scale score is formed: the vectors of reverse-keyed items are multiplied by −1, and all item
vectors are averaged. Negating an item vector flips the sign of every correlation predicted for that
item and leaves its size unchanged, which is exactly what reverse-scoring does. The query is pooled
from the user's items, using the "(R)" marks, and every scale in the database from its items, using
its documented keying. For each database scale, the engine displays the cosine between the two pooled
vectors and sorts the results by its absolute value. In the SurveyBot3000 studies, this value (the
synthetic scale correlation) predicted the empirical correlation between two scales with an accuracy
of *r* = .87 in the pilot study and *r* = .83 in the validation study.

Accuracy summarises all scale pairs at once. A researcher using the search engine asks something
narrower: if a scale in the database is strongly related to mine, will it appear high enough in the
list for me to see it? We answer this question with the data from both studies, and then ask how the
answer changes when the query consists of only a few items, and when reverse-keyed items are not
marked.

# Data

```{r data}
read_study <- function(study, what) {
  read_feather(fetch(glue("{data_url}/{model_name}.raw.{study_tags[[study]]}.{what}.feather")))
}

load_study <- function(study) {
  mapping <- read_study(study, "mapping2") %>% rename(scale_0 = scale0, scale_1 = scale1)
  scales <- read_study(study, "scales")
  human <- read_study(study, "human")
  if (study == "pilot") {
    machine <- as.matrix(read_study(study, "machine"))
  } else {
    emb <- read_feather(fetch(embeddings_url))
    machine <- do.call(cbind, emb$embeddings)
    colnames(machine) <- emb$id
  }
  # items per scale and reverse-keyed items, as in the main analysis
  items_by_scale <- bind_rows(
    scales %>% filter(scale_1 == "") %>%
      left_join(mapping %>% select(-scale_1, -any_of("keyed")), by = c("instrument", "scale_0")),
    scales %>% filter(scale_1 != "") %>%
      left_join(mapping %>% select(-any_of("keyed")), by = c("instrument", "scale_0", "scale_1"))
  )
  items <- split(items_by_scale$variable, items_by_scale$scale)
  if ("keyed" %in% names(mapping)) {
    keyed <- setNames(mapping$keyed, mapping$variable)
    reverse <- map(items, ~ .x[keyed[.x] == -1])
  } else {
    human_cor <- cor(human, use = "p")
    first_key <- setNames(scales$keyed, scales$scale)
    reverse <- imap(items, ~ find_reverse_items_by_first_item(human_cor[.x, .x, drop = FALSE], first_key[[.y]]))
  }
  pairs <- read_study(study, "scale_correlations")
  if (study == "validation") {
    pairs <- pairs %>% filter(lengths(items[scale_a]) >= 3, lengths(items[scale_b]) >= 3)
  }
  instruments <- n_distinct(scales$instrument[scales$scale %in% c(pairs$scale_a, pairs$scale_b)])
  list(human = human, machine = machine, items = items, reverse = reverse, pairs = pairs,
       instruments = instruments)
}

studies <- list(pilot = load_study("pilot"), validation = load_study("validation"))
n_scales <- map_int(studies, ~ n_distinct(c(.x$pairs$scale_a, .x$pairs$scale_b)))
n_pairs <- map_int(studies, ~ nrow(.x$pairs))

# pooling as in the engine: reverse-keyed item vectors negated, then averaged (unit length);
# the displayed value is the cosine of two pooled vectors
scale_vector <- function(s, items, reverse) {
  v <- colMeans(t(s$machine[, items, drop = FALSE]) * ifelse(items %in% reverse, -1, 1))
  v / sqrt(sum(v^2))
}
# empirical scale score: reverse-keyed item responses negated, then averaged
keyed_mean <- function(s, items, reverse) {
  x <- as.matrix(s$human[, items, drop = FALSE])
  x[, items %in% reverse] <- -x[, items %in% reverse]
  rowMeans(x, na.rm = TRUE)
}
displayed_values <- function(s, reverse = s$reverse) {
  scales <- unique(c(s$pairs$scale_a, s$pairs$scale_b))
  vec <- map(set_names(scales), ~ scale_vector(s, s$items[[.x]], reverse[[.x]]))
  map2_dbl(s$pairs$scale_a, s$pairs$scale_b, ~ sum(vec[[.x]] * vec[[.y]]))
}
# the paper's synthetic scale correlation is a Pearson correlation across embedding dimensions;
# check that it equals the engine's cosine
max_difference <- max(map_dbl(studies, ~ max(abs(displayed_values(.x) - .x$pairs$synthetic_r))))
```

We used the scale pairs analysed in the main paper. The pilot study used the holdout data of
Bainbridge et al. (2022): `r studies$pilot$instruments` widely used personality and well-being
questionnaires, `r n_scales["pilot"]` scales and subscales, and `r format(n_pairs["pilot"], big.mark = ",")`
scale pairs, answered by 493 people. The validation study used `r n_scales["validation"]` scales from
`r studies$validation$instruments` questionnaires sampled from APA PsycTests
(`r format(n_pairs["validation"], big.mark = ",")` pairs), answered by 387 people.^[As in the main
paper, the validation analysis includes only scales with at least three items, whereas the pilot
analysis also includes six two-item scales.] Pairs of a scale with one of its own subscales are
excluded. The pilot questionnaires are well known and often published, so the pilot study probably
shows the engine at its best. The validation study is closer to a random draw from the database. We
report the two studies separately. The paper computed the synthetic scale correlation as a Pearson
correlation across the embedding dimensions of the keyed mean vectors. For these scale pairs, it
differs from the engine's cosine by at most `r sub("^0", "", formatC(max_difference, format = "f", digits = 4))`,
so we use the paper's values as displayed values.

We call two scales *strongly related* if their true correlation is at least .70 in absolute value,
and *moderately related* if it is at least .50. A related scale counts as *shown* at a displayed
value *c* if its displayed value has the same sign as the true correlation and is at least *c* in
absolute value. Negative relations therefore count, as long as the engine gets their sign right.

The empirical correlations in the two studies are themselves estimates. With about 400 to 500
participants, a correlation of .50 to .70 has a standard error of about .02 to .04, so pairs close to
.50 or .70 could fall on either side. To take this into account, we drew a plausible true correlation
for every pair from a normal distribution centred on its observed correlation, with its standard
error as the standard deviation, classified all pairs, and repeated this 1,000 times. We report the
median over these repetitions with a 95% interval.

```{r sensitivity-function}
# Share of truly related pairs (|true r| >= t) shown at each display value c, over draws of
# the true correlation from N(observed r, SE). Returns median, 95% interval, and the
# number of truly related pairs.
sensitivity <- function(observed, se, displayed, cutoffs, ts, ndraws = 1000) {
  shown <- array(NA_real_, c(ndraws, length(cutoffs), length(ts)))
  related <- matrix(NA_real_, ndraws, length(ts))
  for (d in seq_len(ndraws)) {
    true <- observed + se * rnorm(length(observed))
    for (j in seq_along(ts)) {
      rel <- abs(true) >= ts[j]
      related[d, j] <- sum(rel)
      signed <- displayed[rel] * sign(true[rel])
      shown[d, , j] <- colMeans(outer(signed, cutoffs, ">="))
    }
  }
  map_dfr(seq_along(ts), function(j) tibble(
    t = ts[j], cutoff = cutoffs,
    share = apply(shown[, , j, drop = FALSE], 2, median),
    lower = apply(shown[, , j, drop = FALSE], 2, quantile, .025),
    upper = apply(shown[, , j, drop = FALSE], 2, quantile, .975),
    related = median(related[, j])))
}

pct <- function(x) sub("^0\\.", ".", formatC(x, format = "f", digits = 2))
study_colours <- c("Pilot study" = "#E69F00", "Validation study" = "#0072B2")  # Okabe-Ito, colourblind-safe
ci <- function(m, l, u) glue("{pct(m)} [{pct(l)}, {pct(u)}]")
```

# How often related scales are shown

```{r sensitivity}
cutoffs <- round(seq(.05, .90, by = .01), 2)
sens <- map_dfr(studies, ~ sensitivity(.x$pairs$empirical_r, .x$pairs$empirical_r_se,
                                       .x$pairs$synthetic_r, cutoffs, c(.50, .70)), .id = "study")
at <- function(st, tt, c) sens %>% filter(study == st, t == tt, abs(cutoff - c) < 1e-9)
of10 <- function(st, tt, c) round(at(st, tt, c)$share * 10)
related_n <- function(st, tt) round(at(st, tt, .30)$related)
```

```{r sensitivity-plot, fig.cap = "Share of related scales shown at or above each displayed value. Lines are medians over 1,000 draws of the true correlations, bands are 95% intervals."}
sens %>%
  filter(cutoff >= .10, cutoff <= .80) %>%
  mutate(t = factor(t, labels = c("Moderately related (|true r| ≥ .50)", "Strongly related (|true r| ≥ .70)")),
         study = factor(study, labels = c("Pilot study", "Validation study"))) %>%
  ggplot(aes(cutoff, share, ymin = lower, ymax = upper, colour = study, fill = study)) +
  geom_ribbon(alpha = .2, colour = NA) +
  geom_line() +
  facet_wrap(~ t) +
  scale_colour_manual(values = study_colours) +
  scale_fill_manual(values = study_colours) +
  scale_x_continuous("Displayed value (absolute)", breaks = seq(.1, .8, by = .1)) +
  scale_y_continuous("Share of related scales shown", limits = c(0, 1)) +
  theme(legend.position = "bottom", legend.title = element_blank())
```

In the validation study, `r of10("validation", .70, .30)` of 10 strongly related scales were shown at
a displayed value of .30 or higher, and `r of10("validation", .70, .40)` of 10 at .40 or higher. In
the pilot study, all strongly related scales reached .40. Moderately related scales needed a lower
displayed value to be seen: at .30, `r of10("validation", .50, .30)` of 10 were shown in the
validation study and `r of10("pilot", .50, .30)` of 10 in the pilot study. These estimates rest on
about `r related_n("validation", .70)` strongly related pairs in the validation study and
`r related_n("pilot", .70)` in the pilot study.

```{r sensitivity-table}
sens %>%
  filter(cutoff %in% c(.30, .40, .50)) %>%
  mutate(value = ci(share, lower, upper), cutoff = paste("Shown at", pct(cutoff))) %>%
  select(study, t, related, cutoff, value) %>%
  pivot_wider(names_from = cutoff, values_from = value) %>%
  mutate(study = str_to_title(study), t = pct(t), related = round(related)) %>%
  rename(Study = study, `|true r| at least` = t, `Related pairs` = related) %>%
  kable(align = "llrrrr", caption = "Share of related scales shown at displayed values of .30, .40 and .50, with 95% intervals.")
```

## How far down the list to read

The same results can be turned around: to see a given share of the related scales, how far down the
result list does a user need to read?

```{r read-down}
read_down <- expand_grid(target = c(.80, .90, .95), sens %>% distinct(study, t)) %>%
  rowwise() %>%
  mutate(cutoff = max(sens$cutoff[sens$study == study & sens$t == t & sens$share >= target])) %>%
  ungroup()
rd <- function(st, tt, target) pct(read_down$cutoff[read_down$study == st & read_down$t == tt & read_down$target == target])
```

```{r read-down-plot, fig.width = 8, fig.height = 6}
plot_data <- read_down %>%
  mutate(panel = factor(t, levels = c(.70, .50),
                        labels = c("Strongly related scales\n(true correlation of .70 or more)",
                                   "Moderately related scales\n(true correlation of .50 or more)")),
         target = factor(paste0(target * 100, "%"), levels = c("80%", "90%", "95%")),
         study = factor(study, levels = c("pilot", "validation"), labels = c("Pilot study", "Validation study")))
study_labels <- plot_data %>% filter(target == "80%", t == .70) %>%
  mutate(cutoff = cutoff + if_else(study == "Pilot study", .035, -.035))

ggplot(plot_data, aes(target, cutoff, colour = study)) +
  geom_line(aes(group = target), colour = "grey80", linewidth = 1.2) +
  geom_point(size = 3.5) +
  geom_text(aes(label = pct(cutoff)), nudge_x = .17, size = 3.8, show.legend = FALSE) +
  geom_text(aes(label = study), data = study_labels, size = 3.8, fontface = "bold", show.legend = FALSE) +
  facet_wrap(~ panel) +
  scale_colour_manual(values = study_colours, guide = "none") +
  scale_x_discrete("Share of related scales the user sees", expand = expansion(add = .5)) +
  scale_y_continuous("Displayed value to read down to", limits = c(.10, .62), breaks = seq(.1, .6, by = .1),
                     labels = pct) +
  labs(title = "How far down the result list to read to see most related scales",
       subtitle = paste("A lower value means reading further down the list. For scales like those in the",
                        "validation study,\nusers had to read much further down than for well-known",
                        "personality questionnaires."),
       caption = paste("Data: SurveyBot3000 pilot study (22 personality and well-being questionnaires, N = 493) and",
                       "validation study\n(57 scales sampled from APA PsycTests, N = 387). Median over 1,000 draws of",
                       "the true correlations; about 45 strongly\nand 180 to 430 moderately related scale pairs per study.")) +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"),
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, colour = "grey40", size = 9),
        plot.caption.position = "plot",
        strip.text = element_text(hjust = 0, face = "bold"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank())
```

To see 9 of 10 strongly related scales, a user needed to read down to `r rd("pilot", .70, .90)` in the
pilot study but to `r rd("validation", .70, .90)` in the validation study. For moderately related
scales, the same share required reading down to `r rd("pilot", .50, .90)` and
`r rd("validation", .50, .90)`. How many results this means depends on the query; the engine shows
the number of results above any displayed value.

```{r compression}
# spread of true and displayed values, and the displayed value expected for a true correlation
# of .70; true-score variance and slope are corrected for sampling error in the empirical r
compression <- map_dfr(studies, function(s) {
  p <- s$pairs
  error_var <- mean(p$empirical_r_se^2)
  reliability <- 1 - error_var / var(p$empirical_r)
  slope <- coef(lm(synthetic_r ~ empirical_r, data = p))[[2]] / reliability
  tibble(sd_true = sqrt(var(p$empirical_r) - error_var),
         sd_displayed = sd(p$synthetic_r),
         at_70 = mean(p$synthetic_r) + slope * (.70 - mean(p$empirical_r)))
}, .id = "study")
cp <- function(st, col) pct(compression[[col]][compression$study == st])
```

The two studies differ this much even though their accuracy is similar (.87 and .83), because
accuracy is a correlation. It shows whether scale pairs are put in the right order relative to each
other, but not whether the displayed values are on the same scale as the true correlations. In the
pilot study they were: the true correlations had a standard deviation of `r cp("pilot", "sd_true")`,
the displayed values one of `r cp("pilot", "sd_displayed")`. In the validation study the displayed
values were compressed toward zero, with a standard deviation of `r cp("validation", "sd_displayed")`
against `r cp("validation", "sd_true")` for the true correlations. A pair with a true correlation of
.70 was displayed at about `r cp("pilot", "at_70")` on average in the pilot study, but at about
`r cp("validation", "at_70")` in the validation study. Most of the difference in how far to read comes
from this compression; the somewhat larger prediction error in the validation study adds a little.
Because the validation study is closer to the database as a whole, its values are the better guide
for how far to read.

# Short queries

```{r query-length, cache = TRUE}
query_pairs <- imap_dfr(studies, function(s, study) {
  scales <- unique(c(s$pairs$scale_a, s$pairs$scale_b))
  vec <- map(set_names(scales), ~ scale_vector(s, s$items[[.x]], s$reverse[[.x]]))
  score <- map(set_names(scales), ~ keyed_mean(s, s$items[[.x]], s$reverse[[.x]]))
  partners <- bind_rows(s$pairs %>% select(query = scale_a, target = scale_b),
                        s$pairs %>% select(query = scale_b, target = scale_a))
  map_dfr(c(1, 2, 3, 5, Inf), function(k) map_dfr(scales, function(q) {
    items <- s$items[[q]]
    if (is.finite(k) && length(items) <= k) return(NULL)
    subsets <- if (is.infinite(k)) list(items)
      else if (choose(length(items), k) <= 10) combn(items, k, simplify = FALSE)
      else unique(map(1:10, ~ sort(sample(items, k))))
    targets <- partners$target[partners$query == q]
    map_dfr(subsets, function(sub) {
      v <- scale_vector(s, sub, s$reverse[[q]])
      h <- keyed_mean(s, sub, s$reverse[[q]])
      tibble(study, k, query = q, target = targets,
             displayed = map_dbl(targets, ~ sum(v * vec[[.x]])),
             observed = map_dbl(targets, ~ cor(h, score[[.x]], use = "p")),
             n = map_int(targets, ~ sum(complete.cases(h, score[[.x]]))))
    })
  }))
}) %>% mutate(se = (1 - observed^2) / sqrt(n - 3))

# compare each subset size with the full scales of the same queries
query_length <- query_pairs %>% filter(is.finite(k)) %>% distinct(study, k) %>%
  pmap_dfr(function(study, k) {
    sub <- query_pairs %>% filter(study == !!study, k == !!k)
    full <- query_pairs %>% filter(study == !!study, is.infinite(k), query %in% sub$query)
    s_sub <- sensitivity(sub$observed, sub$se, sub$displayed, .30, c(.50, .70), ndraws = 500)
    s_full <- sensitivity(full$observed, full$se, full$displayed, .30, c(.50, .70), ndraws = 500)
    tibble(study, k, scales = n_distinct(sub$query),
           accuracy_k = cor(sub$displayed, sub$observed), accuracy_full = cor(full$displayed, full$observed),
           strong_k = s_sub$share[s_sub$t == .70], strong_full = s_full$share[s_full$t == .70],
           moderate_k = s_sub$share[s_sub$t == .50], moderate_full = s_full$share[s_full$t == .50])
  })
ql <- function(st, kk, col) query_length[[col]][query_length$study == st & query_length$k == kk]
```

Users often search with a few items rather than a whole scale. To see what this costs, we took every
scale in both studies, drew random sets of 1, 2, 3 or 5 of its items (up to 10 different sets per
scale), and used each set as a query against every other scale of the same study. For each query we
computed the displayed value from the averaged item vectors, as the engine does, and the empirical
correlation between the mean of the query items and the comparison scale from the raw responses. Only
scales with more items than the query contribute to a row, and each row compares the short queries
with the full versions of the same scales.

```{r query-length-table}
query_length %>%
  arrange(study, k) %>%
  transmute(Study = str_to_title(study), `Query items` = k, Scales = scales,
            Accuracy = glue("{pct(accuracy_k)} ({pct(accuracy_full)})"),
            `Strongly related shown at .30` = glue("{pct(strong_k)} ({pct(strong_full)})"),
            `Moderately related shown at .30` = glue("{pct(moderate_k)} ({pct(moderate_full)})")) %>%
  kable(align = "lrrrrr", caption = "Accuracy (correlation between displayed and empirical values) and share of related scales shown at a displayed value of .30, for queries with few items. Values in parentheses are for the full scales the items were drawn from.")
```

Short queries cost little in the pilot study: even with single items,
`r round(ql("pilot", 1, "strong_k") * 100)`% of the strongly related scales were shown at .30. In the validation study
they cost more. With a single item, accuracy dropped from `r pct(ql("validation", 1, "accuracy_full"))`
to `r pct(ql("validation", 1, "accuracy_k"))`, and `r round(ql("validation", 1, "strong_k") * 10)` of 10
strongly related scales were shown at .30 instead of `r round(ql("validation", 1, "strong_full") * 10)`.
Three items brought accuracy close to that of the full scales (`r pct(ql("validation", 3, "accuracy_k"))`
vs `r pct(ql("validation", 3, "accuracy_full"))`), but still showed fewer strongly related scales at .30
(`r pct(ql("validation", 3, "strong_k"))` vs `r pct(ql("validation", 3, "strong_full"))`). The rows for
three and five items rest on fewer scales, because only longer scales could be shortened that far.

# Unmarked reverse-keyed items

```{r unmarked, cache = TRUE}
set.seed(20260930)
shares <- c(0, .25, .50, .75, 1)
unmarked <- imap_dfr(studies, function(s, study) {
  used <- unique(c(s$pairs$scale_a, s$pairs$scale_b))
  memberships <- imap_dfr(s$reverse[used], ~ tibble(scale = .y, item = .x))
  n_memberships <- nrow(memberships)
  n_scales_reverse <- n_distinct(memberships$scale)
  map_dfr(shares, function(share) {
    map_dfr(seq_len(if (share %in% c(0, 1)) 1 else 50), function(draw) {
      kept <- memberships[sample(nrow(memberships), round((1 - share) * nrow(memberships))), ]
      reverse <- map(set_names(used), ~ kept$item[kept$scale == .x])
      displayed <- displayed_values(s, reverse)
      shown <- sensitivity(s$pairs$empirical_r, s$pairs$empirical_r_se, displayed, .30, c(.50, .70), ndraws = 200)
      tibble(study, share, draw, accuracy = cor(displayed, s$pairs$empirical_r),
             strong = shown$share[shown$t == .70], moderate = shown$share[shown$t == .50])
    })
  }) %>% mutate(memberships = n_memberships, scales_with_reverse = n_scales_reverse)
})
unmarked_summary <- unmarked %>% group_by(study, share, memberships, scales_with_reverse) %>%
  summarise(across(c(accuracy, strong, moderate), median), .groups = "drop")
um <- function(st, sh, col) unmarked_summary[[col]][unmarked_summary$study == st & unmarked_summary$share == sh]
```

The engine can reverse only the items it knows to be reverse-keyed. Users may forget to mark them
with "(R)", and some sources in the database record no keying at all, so their reverse-keyed items
are pooled as if they were positively keyed. To see what this costs, we treated a random share of the
reverse-keyed items as positively keyed (none, a quarter, half, three quarters or all of them; 50
random draws for each intermediate share), pooled the scale vectors again, and compared the new
displayed values with the same empirical correlations as before. In the pilot study,
`r um("pilot", 0, "memberships")` item placements in `r um("pilot", 0, "scales_with_reverse")` scales
are reverse-keyed; in the validation study, `r um("validation", 0, "memberships")` in
`r um("validation", 0, "scales_with_reverse")` scales.

```{r unmarked-table}
unmarked_summary %>%
  arrange(study, share) %>%
  transmute(Study = str_to_title(study), `Reverse-keyed items unmarked` = paste0(share * 100, "%"),
            Accuracy = pct(accuracy), `Strongly related shown at .30` = pct(strong),
            `Moderately related shown at .30` = pct(moderate)) %>%
  kable(align = "llrrr", caption = "Accuracy and share of related scales shown at a displayed value of .30 when a share of the reverse-keyed items is treated as positively keyed (median over random draws).")
```

Accuracy fell steadily with the share of unmarked items. With half of them unmarked, it dropped from
`r pct(um("validation", 0, "accuracy"))` to `r pct(um("validation", .5, "accuracy"))` in the
validation study and from `r pct(um("pilot", 0, "accuracy"))` to `r pct(um("pilot", .5, "accuracy"))`
in the pilot study, and the share of strongly related scales shown at .30 in the validation study
fell from `r round(um("validation", 0, "strong") * 100)`% to `r round(um("validation", .5, "strong") * 100)`%.
With all of them unmarked, accuracy was `r pct(um("validation", 1, "accuracy"))` and
`r pct(um("pilot", 1, "accuracy"))`. The pilot study loses more, as more of its items are
reverse-keyed. How much a single search loses depends on how many reverse-keyed items the query and
the database scale contain.

# Session information

```{r session}
sessionInfo()
```
