---
title: 'Data Cleaning: Larsen Corpus'
author: "Annika Kuelpmann & Laura Juenger"
date: "`r Sys.Date()`"
output:
  html_document:
    code_download: true
    code_folding: show
    highlight: haddock
    theme: flatly
    toc: true
    toc_float: true
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      results = "hold",
                      comment = NA)

```

```{r packages}

library(tidyverse)
library(arrow)
library(knitr)
library(tinytex)
library(markdown)

```

## Overview

This document cleans and preprocesses the Larsen corpus for use in the SYNTH-Net Search project. We separate distinct psychological instruments (e.g., standardized questionnaires, scales, inventories) from vague or generic constructs and items. The aim is to create a cleaned subset of instruments and their respective items that can be added to the SYNTH-Net database.

## To-Do List

### **1. Remaining Scales Subset**

- [x] Check the instrument list manually for false negatives
  (cases where `meta_instrument_name` is actually a valid scale or questionnaire).
- [x] Reclassify false negatives — these should be moved to *instruments*.

---

### **2. Instruments Subset**

- [x] Check the instrument list manually for false positives
  (cases where `meta_instrument_name` refers to a generic or unclear construct, not a formal instrument).
- [x] Reclassify false positives — these should be removed from *instruments*.
- [x] Combine instruments that are essentially the same but differ slightly in naming
  (e.g., versions of AUDIT-10).
  - To do this, you will likely need to compare item counts and items contents.
- [x] Export the cleaned instruments dataset as `.csv` or `.parquet`.
- [ ] Add DOIs for the instruments in the final dataset if available (this will be likely a manual step).  

---

### **How To**

- change and expand the existing R code as needed. 
- you will need the packages arrow and tidyverse, install them if necessary. 
- especially helpful tidyverse functions include:  
  - `filter()` – for subsetting data, filter out rows, creating additional filtering rules  
  - `mutate()` – for reclassification or recoding  
  - `arrange()` – for sorting and inspection  


## Load Data Set

```{r load-data}

# load data set
data <- read_parquet("larsen_data/larsen_corpus.parquet")

```

## Instruments Subset

Create a subset containing only sufficiently defined instruments (questionnaires, scales, inventories) and excluding vague/generic construct names.

```{r defined-subset}

# filter for well-defined instruments using the following criteria:
# 1. Acronym in parentheses (all caps): (BDI), (SDQ)
# 2. Acronym with numbers/hyphens: (PIQ-C), (TAPS-2), (LOT-R)
# 3. Item count: 21-item, 12-item
# 4. Formal instrument keywords: Questionnaire, Scale, Inventory, etc.
# 5. "Test" keyword (case-insensitive, excluding "Testim")
# 6. "questionnaire" lowercase
# 7. Starts with 3+ capital letters: PROMIS, QUALIDEM, TBI-CareQOL
instruments <- data %>%
  filter(
    str_detect(meta_instrument_name, "[(][A-Z]{2,}[)]") |
    str_detect(meta_instrument_name, "[(][A-Z]+-?[A-Z0-9]+[)]") |
    str_detect(meta_instrument_name, "[0-9]+-item") |
    str_detect(meta_instrument_name,
               "Questionnaire|Scale|Inventory|Index|Survey|Checklist|Assessment|Measure") |
    str_detect(meta_instrument_name, "(?i)Test(?!im)") |
    str_detect(meta_instrument_name, "(?i)questionnaire") |
    str_detect(meta_instrument_name, "^[A-Z]{3,}[- ]")
  )

cat("Instruments subset:\n")
cat("- Rows:", nrow(instruments), "\n")
cat("- Unique instruments:", n_distinct(instruments$meta_instrument_name), "\n")

```

```{r instruments-list}

# show instruments in subset
cat("\n\nall instruments in instruments subset:\n")
instrument_names <- instruments %>%
  distinct(meta_instrument_name)

#print(instrument_names, n = Inf)

```

## Remaining Data (Excluded from Instruments Subset)

```{r remaining-subset}

# create remaining data (excluded from well-defined)
# using same refined criteria as above
remaining <- data %>%
  filter(
    !is.na(meta_instrument_name) &
    !str_detect(meta_instrument_name, "[(][A-Z]{2,}[)]") &
    !str_detect(meta_instrument_name, "[(][A-Z]+-?[A-Z0-9]+[)]") &
    !str_detect(meta_instrument_name, "[0-9]+-item") &
    !str_detect(meta_instrument_name, "Questionnaire|Scale|Inventory|Index|Survey|Checklist|Assessment|Measure") &
    !str_detect(meta_instrument_name, "(?i)Test(?!im)") &
    !str_detect(meta_instrument_name, "(?i)questionnaire") &
    !str_detect(meta_instrument_name, "^[A-Z]{3,}[- ]")
  )

cat("Remaining data (excluded from instruments subset):\n")
cat("- Rows:", nrow(remaining), "\n")
cat("- Unique instruments:", n_distinct(remaining$meta_instrument_name), "\n")

```

```{r remaining-instruments-list}

# show all instruments in remaining data
cat("\n\nall instruments
    in remaining data:\n")
instrument_names_remaining <- remaining %>%
  distinct(meta_instrument_name, .keep_all = TRUE)

#print(instrument_names_remaining, n = Inf)

```

```{r new-instruments-list}

#Zeilennummern false negatives
indices_fn <- c(3, 6, 12, 13, 29, 77, 78, 111, 143, 325, 349, 436, 468, 528)

# namen der false negatives aus der distinct-liste extrahieren (basis für index-lookup)
fn_names <- instrument_names_remaining[indices_fn, ] %>%
  pull(meta_instrument_name)

# alle items (nicht nur eine zeile) für diese instrumente aus remaining holen
false_negatives <- remaining %>%
  filter(meta_instrument_name %in% fn_names)

instruments <- bind_rows(instruments, false_negatives)

#doppelte instruments ausschließen
instruments <- instruments %>%
  filter(!meta_instrument_name %in% c(
    "Alcohol Use Disorders Identification Test (10-item) (AUDIT)",
    "EQ-5D-5L (Descriptive system only) (5-item)",
    "Trauma History Questionnaire (THQ)",
    "Stressful Life Events Screening Questionnaire",
    "Everyday Discrimination Scale",
    "The Everyday Discrimination Scale",
    "Satisfaction With Life Scale (SWLS) (5-item)",
    "Satisfaction With Life Scale (SWLS)",
    "Extended Satisfaction With Life Scale",
    "Substance Use Risk Profile Scale (SURPS)",
    "Rosenberg Self-Esteem Scale (10-item) (RSES)",
    "Effort-Reward Imbalance Questionnaire",
    "GAD-7 Generalised Anxiety Disorder Assessment (7-item) (GAD-7)",
    "Generalised Anxiety Disorder Scale (GAD-7)",
    "UCLA loneliness scale version 3",
    "Perceived Stress Scale (10-item)(PSS-10)",
    "PTSD Checklist Civilian Version (PCL-C)",
    "Warwick-Edinburgh Mental Wellbeing Scale (14-item) (WEMWBS)",
    "Warwick-Edinburgh mental well-being scale (WEMWBS)",
    "Patient Health Questionnaire-2 (2-item) (PHQ-2)"
    )
  )

```


```{r undefined-instruments}

# data without instrument info
undefined <- data %>%
  filter(is.na(meta_instrument_name))

cat("Undefined instruments (no instrument name provided):\n")
cat("- Rows:", nrow(undefined), "\n")

```

## Export Data

```{r export}
#export als csv
write_csv(instruments, "larsen_instruments.csv")

# export data in parquet format 
write_parquet(instruments, "larsen_instruments.parquet")

```
