---
title: "SynthNet coverage"
author: "Ruben Arslan"
date: "2023-11-07"
output: 
  html_document:
    toc: true
    toc_float: true
---




```{css, echo=FALSE}
.js-plotly-plot .plotly svg a { 
  fill: inherit !important 
}
```

```{js, echo=FALSE}
document.addEventListener("DOMContentLoaded", function() {
    const plotElements = document.querySelectorAll('.plotly.html-widget'); // Gets all Plotly widgets
    const firstPlot = plotElements[0]; // Gets the first Plotly plot

    Plotly.update(firstPlot).then(gd => {
        gd.on('plotly_treemapclick', () => false); // Example: removing treemap click event
    });
});
```


```{r warning=F,message=F}
knitr::opts_chunk$set(echo = TRUE, error = T, warning = F, message = F)

# Libraries and Settings

# Libs ---------------------------
library(reticulate)
library(tidyverse)
library(plotly)
source("paths.R")
# reticulate::py_install(
#   packages = c("numpy", "plotly", "kaleido==0.2.1"), 
#   envname = "r-reticulate-test",
#   pip = TRUE
# )
# reticulate::conda_install('r-reticulate-test', 'plotly', channel = 'plotly')
try(reticulate::use_miniconda(RETICULATE_ENV))
# plotly 4.11 save_image() checks py_available() but never initializes python itself
try(invisible(reticulate::py_available(initialize = TRUE)))

# Coverage = tests for which SynthNet has scale-structured item data,
# i.e. at least one extracted item assigned to a scale (bucket == "scaled").
# Items in buckets "orphan" (extracted but not claimed by any scale) and
# "unscaled" (explicitly scale-free, e.g. demographics) do not count.
# PsycTests DOI is derived from the PDF filename (accession number 9999NNNNN -> 10.1037/tNNNNN-000).
synthnet_dois <- arrow::open_dataset("data/raw-extractions-exploded.parquet") %>%
  filter(bucket == "scaled") %>%
  distinct(path) %>%
  collect() %>%
  mutate(DOI = str_c("10.1037/t", str_sub(str_extract(basename(path), "^[0-9]+"), 5, 9), "-000")) %>%
  distinct(DOI)
psyctests <- readRDS(PSYC_RECORDS)
psyctests_info <- readRDS(PSYC_INFO)
psyctests_usage_by_test <- psyctests_info %>% group_by(DOI, Name) %>% summarise(usage_count = sum(usage_count, na.rm = T)) %>% ungroup()
```

## Coverage in terms of number of tests in APA PsycTests
```{r}
psyctests <- psyctests %>% mutate(present_in_synthnet = DOI %in% synthnet_dois$DOI)
psyctests %>% 
  mutate(total_tests = n_distinct(DOI)) %>%  
  group_by(present_in_synthnet) %>% 
  summarise(tests_count = n_distinct(DOI),
            tests_percentage = tests_count/first(total_tests))
```


## Coverage in terms of usage and number of tests in APA PsycTests
```{r}
psyctests_usage_by_test <- psyctests_usage_by_test %>% mutate(present_in_synthnet = DOI %in% synthnet_dois$DOI)

psyctests_usage_by_test %>% 
  mutate(total_count = sum(usage_count, na.rm = T), 
         total_tests = n_distinct(DOI)) %>%  
  group_by(present_in_synthnet) %>% 
  summarise(usage_count = sum(usage_count, na.rm = T),
            usage_percentage = usage_count/first(total_count),
            tests_count = n_distinct(DOI),
            tests_percentage = tests_count/first(total_tests),
            first(total_tests))
```

## By instrument type broad
```{r}
psyctests_usage_by_test <- psyctests_usage_by_test %>% mutate(present_in_synthnet = DOI %in% synthnet_dois$DOI) %>% left_join(psyctests %>% select(DOI, instrument_type_broad), by = "DOI")

psyctests_usage_by_test %>% 
  group_by(instrument_type_broad) %>% 
  mutate(total_count = sum(usage_count, na.rm = T), 
         total_tests = n_distinct(DOI)) %>%  
  group_by(instrument_type_broad, present_in_synthnet) %>% 
  summarise(usage_count = sum(usage_count, na.rm = T),
            usage_percentage = usage_count/first(total_count),
            tests_count = n_distinct(DOI),
            tests_percentage = tests_count/first(total_tests))
```

## Coverage over time
```{r}
psyctests_info <- psyctests_info %>% mutate(present_in_synthnet = DOI %in% synthnet_dois$DOI)

by_year <- psyctests_info %>% 
  filter(usage_count > 0) %>% 
  group_by(Year) %>% 
  mutate(total_count = sum(usage_count, na.rm = T), 
         total_tests = n_distinct(DOI)) %>%  
  group_by(Year, present_in_synthnet) %>% 
  summarise(usage_count = sum(usage_count, na.rm = T),
            usage_percentage = usage_count/first(total_count),
            tests_count = n_distinct(DOI),
            tests_percentage = tests_count/first(total_tests))

ggplot(by_year %>% filter(present_in_synthnet), aes(Year, usage_percentage)) + geom_smooth(color = "orange") + geom_point() +
  theme_bw()
```

## Top missing
```{r}
psyctests_usage_by_test %>% filter(!present_in_synthnet) %>% 
  arrange(desc(usage_count)) %>% 
  DT::datatable()
```


```{r}


theme_set(theme_minimal(base_size = 14))

psyctests_info <- psyctests_info %>% 
  left_join(psyctests %>% select(DOI, Acronym = first_acronym), by = "DOI") %>% 
  mutate(shortName = coalesce(Acronym, Name)) %>% 
  mutate(shortName = case_when(
    Name == "trail making test" ~ "TMT",
    Name == "alcohol use disorders identification test" ~ "AUDIT",
    Name == "perceived stress scale" ~ "PSS",
    Name == "perceived stress scale" ~ "PSS",
    Name == "beck anxiety inventory" ~ "BAI",
    Name == "positive and negative affect scale" ~ "PANAS-B",
    Name == "center for epidemiological studies depression scale" ~ "CESD",
    Name == "stroop color and word test" ~ "SCWT",
    Name == "clinician-administered ptsd scale" ~ "CAPS",
    shortName == "WHO WMH-CIDI" ~ "WMH-CIDI",
    Name == "barthel index" ~ "ADL",
    Name == "stroop color and word test" ~ "SCWT",
    TRUE ~ shortName
  ))

tests <- psyctests_info %>% 
  group_by(DOI, shortName, Name, present_in_synthnet) %>%  
  summarise(n = sum(usage_count, na.rm = T),
            parent = "") %>% 
  ungroup() %>% 
  arrange(runif(n()))
```

```{r}
source("treemap_functions.R")

pal <- readRDS("data/palette.rds")

pal <- rep(pal, length.out = nrow(tests) + 1)
pal <- if_else(c(F,tests$present_in_synthnet), pal, "#EEE")
tibble(color = as.vector(pal[-1]), synth = tests$present_in_synthnet, Name = tests$Name, n = tests$n) %>% 
  arrange(desc(n))

p <- treemap_graph(tests, colors = pal)

try(save_image(p, "figures/treemap_coverage.png", width = 1400, height = 700,
           scale = 5))

p
```

## Coverage by source: SynthNet + scale hunt + SemanticNet

Colored = SynthNet scale-structured coverage (original palette); orange = our
web scale hunt (`data/restricted/scale-hunt-extractions-exploded.parquet`);
blue = SemanticNet fills (Rosenbusch et al., `semanticnet_ingest.R`, reading the
export repaired by `semanticnet_clean.py` / `semanticnet_match.py`);
green = Larsen/aligns public-repository fills (`aligns_ingest.R`); grey = missing.
Fill tiers are content-deduplicated for the search engine (`dedupe_fill_tiers.R`:
records whose item set is near-identical, Jaccard ≥ .8, to a sibling PsycTests
record already in the corpus are dropped; short forms stay). Deduplicated DOIs
still count as covered here — their items are in the corpus under the sibling
record listed in `data/processed/fill_tier_dedupe_aliases.csv`.

```{r}
source("scale_hunt_treemap.R")
p
```


## Total coverage (sources pooled)

Same treemap, but coverage is binary: every record covered by any source
(SynthNet, scale hunt, SemanticNet, Larsen/aligns) gets the original colourful
palette, missing records stay grey. Built in `scale_hunt_treemap.R`, which is
already sourced above.

```{r}
p_all
```
