---
title: "Corpus descriptives for the revision"
author: "Ruben Arslan"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
---

Descriptive statistics of the SynthNet search corpus requested for the
manuscript revision. Inputs are the exploded-item parquets (one row per item
per scale membership): Björn's extractions (`data/raw-extractions-exploded.parquet`,
bucket `scaled`) and the three fill tiers (hunt, SemanticNet, aligns). All of
them are local-only; see `README.md`.

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(dplyr); library(tidyr); library(stringr); library(arrow); library(knitr)
source("paths.R")

doi_from_path <- function(path) {
  str_c("10.1037/t", str_sub(str_extract(basename(path), "[0-9]{9}"), 5, 9), "-000")
}
cols <- c("path", "bucket", "scale_id", "scale_name", "scale_id_path", "scale_depth",
          "item_item_id", "item_reverse_coded")

load_tier <- function(file, tier, dataset = FALSE) {
  d <- if (dataset) open_dataset(file) else read_parquet(file)
  d %>% select(all_of(cols)) %>% collect() %>% mutate(tier = tier)
}
items <- bind_rows(
  load_tier("data/raw-extractions-exploded.parquet", "synthnet", dataset = TRUE) %>% filter(bucket == "scaled"),
  load_tier("data/restricted/scale-hunt-extractions-exploded.parquet", "hunt"),
  load_tier("data/semanticnet/semanticnet-extractions-exploded.parquet", "semanticnet"),
  load_tier("data/aligns/aligns-extractions-exploded.parquet", "aligns")
) %>%
  mutate(DOI = doi_from_path(path),
         scale_depth = coalesce(scale_depth, 1))
```

## Unit of analysis

A row is one item assigned to one scale. `scale_id_path` lists the scale and
its ancestors, so an item that belongs to a subscale is counted for that
subscale and, via the path, for its parent scale(s). Three counts are
reported:

- **per instrument** (PsycTests record): distinct items in the record;
- **per scale node, own items only**: items assigned directly to the scale
  (for a parent scale, only items not assigned to any subscale);
- **per scale node, including subscales**: items assigned to the scale or any
  scale below it, which is the count that matters when items are pooled into
  one embedding per scale.

```{r structure}
items %>% count(tier, name = "rows") %>%
  left_join(items %>% distinct(tier, DOI) %>% count(tier, name = "instruments"), by = "tier") %>%
  left_join(items %>% distinct(tier, DOI, scale_id) %>% count(tier, name = "scale_nodes"), by = "tier") %>%
  left_join(items %>% distinct(tier, DOI, item_item_id) %>% count(tier, name = "distinct_items"), by = "tier") %>%
  kable(caption = "Corpus size by tier")
items %>% distinct(tier, DOI, scale_id, scale_depth) %>% count(tier, scale_depth) %>%
  pivot_wider(names_from = scale_depth, values_from = n, values_fill = 0) %>%
  kable(caption = "Scale nodes by depth (1 = top-level scale)")
```

```{r counts}
per_instrument <- items %>% distinct(tier, DOI, item_item_id) %>% count(tier, DOI, name = "n_items")

per_node_own <- items %>% distinct(tier, DOI, scale_id, item_item_id) %>%
  count(tier, DOI, scale_id, name = "n_items")

# an item counts for every scale on its path
per_node_incl <- items %>%
  select(tier, DOI, scale_id_path, item_item_id) %>%
  unnest(scale_id_path) %>%
  distinct(tier, DOI, scale_id = scale_id_path, item_item_id) %>%
  count(tier, DOI, scale_id, name = "n_items")

depth <- items %>% distinct(tier, DOI, scale_id, scale_depth)
per_node_own <- per_node_own %>% left_join(depth, by = c("tier", "DOI", "scale_id"))
per_node_incl <- per_node_incl %>% left_join(depth, by = c("tier", "DOI", "scale_id"))

describe <- function(x) {
  tibble(n = length(x), mean = mean(x), sd = sd(x), median = median(x),
         q10 = quantile(x, .1), q25 = quantile(x, .25), q75 = quantile(x, .75), q90 = quantile(x, .9),
         min = min(x), max = max(x), share_1_item = mean(x == 1), share_le_3 = mean(x <= 3))
}
summ <- function(df, ...) {
  bind_rows(
    df %>% summarise(describe(n_items), .by = c(...)),
    df %>% summarise(describe(n_items)) %>% mutate(tier = "all")
  )
}
```

## Items per instrument

```{r}
summ(per_instrument, tier) %>% mutate(across(where(is.numeric), ~ round(.x, 2))) %>% kable()
```

## Items per scale node, own items only

```{r}
summ(per_node_own, tier) %>% mutate(across(where(is.numeric), ~ round(.x, 2))) %>% kable()
per_node_own %>% filter(tier == "synthnet") %>% summarise(describe(n_items), .by = scale_depth) %>%
  arrange(scale_depth) %>% mutate(across(where(is.numeric), ~ round(.x, 2))) %>% kable(caption = "SynthNet tier, by depth")
```

## Items per scale node, including subscales

This is the number of item embeddings pooled into a scale vector.

```{r}
summ(per_node_incl, tier) %>% mutate(across(where(is.numeric), ~ round(.x, 2))) %>% kable()
per_node_incl %>% filter(tier == "synthnet") %>% summarise(describe(n_items), .by = scale_depth) %>%
  arrange(scale_depth) %>% mutate(across(where(is.numeric), ~ round(.x, 2))) %>% kable(caption = "SynthNet tier, by depth")
```

## Headline

```{r}
all_incl <- per_node_incl$n_items
all_own <- per_node_own$n_items
all_inst <- per_instrument$n_items
cat(sprintf("Across the whole corpus (%s instruments, %s scale nodes):\n",
            format(length(all_inst), big.mark = ","), format(length(all_incl), big.mark = ",")))
cat(sprintf("  items per instrument:                     mean %.1f, median %d\n", mean(all_inst), as.integer(median(all_inst))))
cat(sprintf("  items per scale (incl. subscales):        mean %.1f, median %d\n", mean(all_incl), as.integer(median(all_incl))))
cat(sprintf("  items per scale (own items only):         mean %.1f, median %d\n", mean(all_own), as.integer(median(all_own))))
cat(sprintf("  scales with a single item (incl. subscales): %.1f %%\n", 100 * mean(all_incl == 1)))
```

```{r write}
out <- bind_rows(
  summ(per_instrument, tier) %>% mutate(unit = "instrument"),
  summ(per_node_own, tier) %>% mutate(unit = "scale_node_own_items"),
  summ(per_node_incl, tier) %>% mutate(unit = "scale_node_incl_subscales")
) %>% select(unit, tier, everything())
write.csv(out, "data/processed/descriptives_items_per_scale.csv", row.names = FALSE)
```
