---
title: "Supplementary Note: Item sources beyond the APA PsycTests extractions"
format:
  docx:
    # no heading ids: they become section-wide bookmarks, which Word shows as gray brackets
    from: markdown-auto_identifiers
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(stringr)
library(tidyr)
library(readr)
library(arrow)
library(jsonlite)
library(purrr)

# Run from analyses/corpus_coverage/. Local-only inputs (restricted item text, licensed PsycTests
# tables, SynthNet extractions) are listed in README.md; PSYC_RECORDS / PSYC_INFO come from paths.R.
source("paths.R")
p <- function(...) file.path("data", ...)
fmt <- function(x) format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
pc <- function(x) sprintf("%.1f%%", 100 * x)
doi_from_path <- function(path) {
  str_c("10.1037/t", str_sub(str_extract(basename(path), "[0-9]{9}"), 5, 9), "-000")
}
```

```{r coverage}
# as in coverage_by_source.R of the corpus coverage pipeline
records <- readRDS(PSYC_RECORDS)
usage <- readRDS(PSYC_INFO) %>%
  group_by(DOI) %>% summarise(usage_count = sum(usage_count, na.rm = TRUE), .groups = "drop") %>%
  filter(usage_count > 0)  # 26 DOIs have rows with only NA usage
n_records <- n_distinct(records$DOI)
n_used <- nrow(usage)
total_usage <- sum(usage$usage_count)

hunt <- read_parquet(p("restricted", "scale-hunt-extractions-exploded.parquet"))
semnet <- read_parquet(p("semanticnet", "semanticnet-extractions-exploded.parquet"))
aligns <- read_parquet(p("aligns", "aligns-extractions-exploded.parquet"))
aliases <- read_csv(p("processed", "fill_tier_dedupe_aliases.csv"), show_col_types = FALSE)

extraction_dois <- open_dataset(p("raw-extractions-exploded.parquet")) %>%
  filter(bucket == "scaled") %>% distinct(path) %>% collect() %>%
  mutate(DOI = doi_from_path(path)) %>% pull(DOI) %>% unique()
fill_dois <- function(d, tier) union(unique(doi_from_path(d$path)), aliases$dropped_DOI[aliases$dropped_tier == tier])
hunt_dois <- fill_dois(hunt, "hunt")
semnet_dois <- fill_dois(semnet, "semanticnet")
aligns_dois <- fill_dois(aligns, "aligns")
semnet_all <- union(semnet_dois, read_csv(p("processed", "semanticnet_matches_all.csv"), show_col_types = FALSE)$DOI)
aligns_all <- union(aligns_dois, read_csv(p("processed", "aligns_matches_all.csv"), show_col_types = FALSE)$DOI)

added <- list(
  extractions = extraction_dois,
  hunt = setdiff(hunt_dois, extraction_dois),
  semnet = setdiff(semnet_dois, union(extraction_dois, hunt_dois)),
  aligns = setdiff(aligns_dois, Reduce(union, list(extraction_dois, hunt_dois, semnet_dois))))
alone <- list(extractions = extraction_dois, hunt = hunt_dois, semnet = semnet_all, aligns = aligns_all)
covered <- function(dois) {
  dois <- intersect(dois, records$DOI)
  c(n = length(dois), records = length(dois) / n_records,
    use = sum(usage$usage_count[usage$DOI %in% dois]) / total_usage)
}
cov_added <- map(added, covered)
cov_alone <- map(alone, covered)
cov_all <- covered(Reduce(union, added))
cov_after_hunt <- covered(union(extraction_dois, hunt_dois))

instruments <- function(d) n_distinct(d$path)
items <- function(d) n_distinct(paste(d$path, d$item_item_id))
```

# Supplementary Note 6

Most of the search corpus consists of items extracted from the documentation of APA PsycTests
records. Many frequently used instruments are missing from these extractions, typically because
PsycTests holds no item text for them, occasionally because we could not extract it. To measure how
much this matters, we weighted each PsycTests record by how often the instrument is used according to
the APA PsycInfo database. PsycTests contains `r fmt(n_records)` records, of which `r fmt(n_used)`
have been used at least once. So, the item data we could extract from PsycTests covered
`r pc(cov_added$extractions["records"])` of the records but only `r pc(cov_added$extractions["use"])`
of all documented uses. We added items from three further sources: a targeted retrieval of the
most-used missing instruments from the open web, the item database of the Semantic Scale Network
(Rosenbusch et al., 2020), and the item corpus compiled for ALIGNS (Larsen et al., 2025). Items from
each source were assigned to a PsycTests record. A source only filled records that no earlier source
already covered, in the order extractions, web retrieval, Semantic Scale Network, ALIGNS. Together,
the four sources cover `r pc(cov_all["records"])` of the records and `r pc(cov_all["use"])` of uses
(Table S1).

```{r table-s1}
row <- function(label, key, d = NULL) {
  tibble(Source = label,
         `Instruments added` = if (is.null(d)) fmt(cov_added[[key]]["n"]) else fmt(instruments(d)),
         `Items added` = if (is.null(d)) "" else fmt(items(d)),
         `Records covered, added` = glue::glue("{fmt(cov_added[[key]]['n'])} ({pc(cov_added[[key]]['records'])})"),
         `Records covered, this source alone` = glue::glue("{fmt(cov_alone[[key]]['n'])} ({pc(cov_alone[[key]]['records'])})"),
         `Share of use, added` = pc(cov_added[[key]]["use"]),
         `Share of use, alone` = pc(cov_alone[[key]]["use"]))
}
bind_rows(
  row("PsycTests extractions", "extractions"),
  row("Web retrieval", "hunt", hunt),
  row("Semantic Scale Network", "semnet", semnet),
  row("ALIGNS item corpus", "aligns", aligns),
  tibble(Source = "All sources", `Instruments added` = "", `Items added` = "",
         `Records covered, added` = glue::glue("{fmt(cov_all['n'])} ({pc(cov_all['records'])})"),
         `Records covered, this source alone` = "", `Share of use, added` = pc(cov_all["use"]),
         `Share of use, alone` = "")
) %>%
  knitr::kable(caption = "Table S1. Coverage of PsycTests records and of their use in PsycInfo by source.")
```

*Note.* Percentages of records are shares of all `r fmt(n_records)` PsycTests records. Share of use
is the share of PsycInfo uses of PsycTests instruments that falls on covered records. "Added" counts
only records not covered by a source higher in the table; "this source alone" counts every record the
source could cover, regardless of the other sources. Records covered can exceed instruments added
because records removed as duplicates of an instrument already in the corpus still count as covered
(see Translations and duplicates).

## Web retrieval of the most-used missing instruments

```{r hunt}
# the committed target list carries no PsycTests fields; instrument type and commercial status
# come from the local PsycTests records
targets <- read_csv(p("processed", "scale_hunt_targets.csv"), show_col_types = FALSE) %>%
  select(DOI) %>%
  left_join(records %>% distinct(DOI, .keep_all = TRUE) %>% select(DOI, instrument_type_broad, Commercial),
            by = "DOI")
n_targets <- nrow(targets)
n_questionnaires <- sum(targets$instrument_type_broad == "questionnaire")
n_commercial <- sum(targets$Commercial == "Yes", na.rm = TRUE)
n_targets_covered <- sum(targets$DOI %in% hunt_dois)

runs <- list.files(p("restricted"), "^(batch.*|pilot_raw_workflow_output)[.]json$", full.names = TRUE)
run_info <- map(runs, ~ fromJSON(.x, simplifyVector = FALSE))
n_agents <- sum(map_dbl(run_info, ~ .x$agentCount %||% 0))
n_final_pass <- length(fromJSON(p("restricted", "batch09_results.json"), simplifyVector = FALSE)$result)

# checker verdict per record: the best one over repeated attempts
check <- read_csv(p("processed", "scale_hunt_check_report.csv"), show_col_types = FALSE) %>%
  mutate(rank = match(str_extract(status, "^[a-z_A-Z]+"), c("ok", "REVIEW", "no_source_text", "not_found"))) %>%
  filter(!is.na(rank)) %>%
  group_by(doi) %>% slice_min(rank, n = 1, with_ties = FALSE) %>% ungroup()
n_ok <- sum(check$rank == 1)
n_review <- sum(check$rank == 2)
n_scan <- sum(check$rank == 3)
n_extracted <- n_ok + n_review + n_scan
# items whose text, options and notes are all too short (<= 12 normalised characters) to locate
n_short <- if ("checkable" %in% names(check)) sum(check$items - check$checkable, na.rm = TRUE) else 0

hunt_items <- hunt %>% distinct(path, item_item_id, item_reverse_coded)
n_reverse <- sum(hunt_items$item_reverse_coded %in% TRUE)
n_reverse_instruments <- n_distinct(hunt_items$path[hunt_items$item_reverse_coded %in% TRUE])
```

We listed the `r n_targets` most-used PsycTests records without scale-structured item data:
`r n_questionnaires` questionnaires and `r n_targets - n_questionnaires` other rating instruments, of
which `r n_commercial` are commercially distributed. For each record, a language model agent searched
the open web for the items, using a web search engine, the public bibliographic databases OpenAlex,
Crossref and Semantic Scholar, and direct downloads from official instrument websites, journal
appendices, author-archived documents and measure repositories. Agents were not allowed to bypass
logins or use institutional access. Each agent saved every source it used and extracted the items
verbatim from that saved source, with their original numbering, subscale assignment, response options
and reverse keying where the source stated them. Agents were told never to reconstruct items from
memory. When the first agent returned nothing usable, a second, more capable agent tried again. The
first pass used Claude Haiku 4.5, the second Claude Sonnet 5 (both Anthropic). A final pass on
`r n_final_pass` remaining targets used Claude Sonnet 5 with a hand-written hint per instrument (the
original publication, known hosting sites, version pitfalls). The agents ran as multi-agent workflows
in Claude Code; in total, at least `r n_agents` agents were run.

A script then compared the extracted items with the text of the saved source after normalising case,
punctuation and whitespace; `r n_short` items too short to locate reliably (e.g., single adjectives)
were not checked. Of the `r n_targets_covered` records with extracted items, `r n_extracted` went
through this check. It found at least 90% of the checkable items in the source for `r n_ok`. For
`r n_review` it found fewer, partly because it also compared the agents' administration notes, which
often contained commentary absent from the source.
For `r n_scan` records the saved source was a scan without a text layer; two of these (the Conflict
Tactics Scales and the State-Trait Anxiety Inventory for Children) we checked by eye against the page
images.

After removing translation mismatches and duplicates, `r instruments(hunt)` instruments with
`r fmt(items(hunt))` items remained, covering `r n_targets_covered` of the `r n_targets` targets.
Coverage of uses rose from `r pc(cov_added$extractions["use"])` to `r pc(cov_after_hunt["use"])`,
while coverage of records rose only from `r pc(cov_added$extractions["records"])` to
`r pc(cov_after_hunt["records"])`. The other `r n_targets - n_targets_covered` targets could not be
retrieved from the open web, mostly commercial instruments (for example the MMPI-2, CPI, NEO PI, PAI
and the Wechsler, Bayley and Vineland batteries). Retrieved item text is stored locally and not
redistributed; the published dataset contains only the pooled scale vectors.

## Semantic Scale Network

```{r semnet}
ssn_items <- nrow(read.csv(p("semanticnet", "items_clean.csv")))
ssn_scales <- read_csv(p("semanticnet", "scale_matches.csv"), show_col_types = FALSE)
ssn_manual <- nrow(read_csv(p("processed", "semanticnet_scale_exclusions.csv"), show_col_types = FALSE))
```

The Semantic Scale Network (Rosenbusch et al., 2020) is an online tool that detects semantic overlap
between psychological scales. Hannes Rosenbusch provided the underlying item database:
`r fmt(ssn_items)` items from `r fmt(nrow(ssn_scales))` scales. Of the `r fmt(nrow(ssn_scales))` scales, `r sum(ssn_scales$match_type != "none")`
could be matched to a PsycTests record by name. We did not match scales whose name does not identify
a published instrument: facet scales from the IPIP proxy keys of other inventories (e.g., "insight")
and modules of survey archives (ARDA, the LISS panel). A match had to be distinctive (a name of at
least three words or 20 characters, or one that equals the PsycTests name apart from generic words
such as "scale" and numbers), and the number of items had to be within 25% of the item count listed
in PsycTests. Each scale went to its best match among all such records, the most used one. If that
record was a translation or already covered by an earlier source, the scale added nothing rather than
going to a lesser match. On review, `r ssn_manual` scales matched a different instrument of the same
name; we excluded them by hand. This added `r cov_added$semnet["n"]`
records, `r instruments(semnet)` after removing duplicates, with `r fmt(items(semnet))` items. The
database records neither subscales, response options nor reverse keying.

## ALIGNS item corpus

```{r aligns}
larsen <- read_csv(p("aligns", "larsen_instruments.csv"), show_col_types = FALSE)
```

ALIGNS (Larsen et al., 2025) compiled questionnaire items from public measure repositories: the NIH
HEAL common data elements, the Catalogue of Mental Health Measures, the Science of Behavior Change
measures repository, the Stress Measurement Network and PROMIS. We separated formal instruments from
generic item sets and merged versions of the same instrument, which left `r fmt(nrow(larsen))` items
from `r n_distinct(larsen$meta_instrument_name)` instruments. These were matched to PsycTests records
by exact name or by the core of the name (at least two words), again requiring the number of items to
be within 25% of the PsycTests record, and each went to its most used match, as above. Version labels
in parentheses were not used for matching, and five matches that passed these checks paired the wrong
versions, so we removed them by hand. This added `r cov_added$aligns["n"]` records,
`r instruments(aligns)` instruments with `r fmt(items(aligns))` items after removing duplicates. Like
the Semantic Scale Network, the corpus records no reverse keying or response options.

## Translations and duplicates

```{r dedupe}
dropped <- count(aliases, dropped_tier)
n_dropped <- function(tier) dropped$n[dropped$dropped_tier == tier]
```

PsycTests holds separate records for translated versions of an instrument ("... –Chinese version").
Because matching relied on names, English items could have been assigned to a translation record when
the English original was already covered. The two name-matched sources therefore never filled records
whose names mark a translation, and an instrument whose best match was a translation added nothing.

Several added instruments turned out to duplicate one already in the corpus under a different record,
typically because the extractions had taken the English items from a study validating a translation
and filed them under the translation's record. We compared the normalised item text of every added
instrument with every instrument already in the corpus and removed added instruments whose items
overlapped by at least 80% (Jaccard similarity). This removed `r nrow(aliases)` instruments
(`r n_dropped("hunt")` from web retrieval, `r n_dropped("semanticnet")` from the Semantic Scale
Network, `r n_dropped("aligns")` from ALIGNS). An instrument whose items were a subset of another's,
such as the PHQ-9 within the full PHQ, counts as a separate instrument and was kept.

## Use in the search engine

The search engine pools items from all four sources in the same way and records the source of each
item. Items without reverse-keying information are treated as positively keyed. This affects the
Semantic Scale Network and ALIGNS instruments, which record no keying, and web-retrieved instruments
whose source did not state it (`r n_reverse` of the `r fmt(items(hunt))` web-retrieved items, in
`r n_reverse_instruments` instruments, are marked as reverse-keyed). In these instruments, any
reverse-keyed items enter the scale vector unreversed. The lack of keying information is flagged in
the interface. The checks of extracted items against the
PsycTests documentation used for the main corpus do not apply to the three additional sources.

## References

Larsen, K. R., Yan, S., Mueller, R. M., Sang, L., Rönkkö, M., Starzl, R., & Edmondson, D. (2025).
*ALIGNS: Unlocking nomological networks in psychological measurement through a large language model*
\[Preprint\]. arXiv. https://arxiv.org/abs/2509.09723

Rosenbusch, H., Wanders, F., & Pit, I. L. (2020). The Semantic Scale Network: An online tool to
detect semantic overlap of psychological scales and prevent scale redundancies. *Psychological
Methods, 25*(3), 380–392.
